%% Master CV - Michael J. Marrujo
%% Comprehensive overview of all competencies, experience, and achievements.
%% Use as a master reference when tailoring role-specific CVs (cv/main_<company>.tex).
%%
%% Compile with: lualatex main_example.tex
%% (pdflatex often fails on modern MiKTeX with fontawesome5 font-expansion errors.)
%%
%% TODO: add your GitHub URL to \extrainfo below once you have one.

\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

% Force both first and last name AND section headings to render in moderncv
% blue (color1). Default banking on lualatex+MiKTeX leaves these black, which
% looks inconsistent with the rest of the blue accent scheme.
\renewcommand*{\firstnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\lastnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\sectionstyle}[1]{{\sectionfont\color{color1}#1}}

\usepackage[utf8]{inputenc}
\usepackage{needspace}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    pdftitle={Michael J. Marrujo - CV},
    pdfpagemode=FullScreen,
}
\usepackage[scale=0.80]{geometry}
\usepackage{import}

% personal data
\name{Michael}{Marrujo}
\address{Orange County, CA, USA}{}{}
\phone[mobile]{714-321-4564}
\email{michaelmarrujo3@gmail.com}
\extrainfo{\href{https://www.linkedin.com/in/mmarrujo3/}{LinkedIn}}

\begin{document}

\makecvtitle

% ============================================================
%     PROFILE STATEMENT  (tailor this per role when copying to main_<company>.tex)
% ============================================================

\vspace{6pt}
\small{AI implementer at the intersection of business operations and software. Led a company-wide AI rollout at a \$40M manufacturer while building the full-stack web applications those workflows run on, and founded an AI consulting practice with live client deliverables. Fluent translating between the C-suite and the floor, and comfortable owning an initiative from a vague business problem all the way to shipped, in-production software.}

% ============================================================
%     CORE COMPETENCIES
% ============================================================

\section{Core Competencies}
\vspace{1pt}
\begin{itemize}
\item \textbf{AI Adoption \& Enablement}: Org-wide Claude \& Gemini rollout, internal training on prompt and workflow design, moving a dev team onto Claude Code.
\item \textbf{Full-Stack Development}: Shipping production web apps from scratch in JavaScript, HTML/CSS, and Google Apps Script; GitHub, Replit.
\item \textbf{Business Operations}: Process mapping, workflow redesign, and cross-functional requirements gathering across sales, finance, logistics, and purchasing.
\item \textbf{Stakeholder Alignment}: Translating between executives and operators; teaching non-technical teams to adopt new tools.
\item \textbf{Tooling}: Claude, Claude Code, Gemini, ChatGPT, Excel, data visualization.
\end{itemize}

% ============================================================
%     PROFESSIONAL EXPERIENCE
% ============================================================

\section{Professional Experience}
\vspace{3pt}
\begin{itemize}

\needspace{5\baselineskip}
\item{\cventry{2026--Present}{Founder \& Principal Consultant}{Theron Digital}{Orange County, CA}{}{\vspace{1pt}
\begin{itemize}
    \item Founded and run an AI-enabled consulting practice: incorporated the LLC, built the marketing website (HTML/CSS/JavaScript), and publish content that generates inbound interest.
    \item Scoped and built a custom profitability web application for a \$5M landscape-services client to surface margin drivers across service lines and inform pricing.
\end{itemize}}}

\vspace{3pt}

\needspace{5\baselineskip}
\item{\cventry{2024--Present}{AI Strategist (2026--Present) / Business Operations Analyst (2024--2025)}{Container Supply Company}{Garden Grove, CA}{}{\vspace{1pt}
\begin{itemize}
    \item Designed and built from scratch a full-stack web application (JavaScript, HTML/CSS) replacing the paper-based order workflow at a \$40M manufacturer; rearchitected the order structure with sales, logistics, finance, and purchasing leadership, eliminating recurring C-suite-to-floor escalations.
    \item Own the company's AI adoption: ran the Claude and Gemini rollout, taught the internal training on prompt and workflow design, and brought the dev team onto Claude Code; consolidated 30 unused licenses for \$6K in annual savings.
    \item Building a full-stack maintenance app in-house (vs. \$36K off-the-shelf software) to replace a Google Sheets system and clear SQF certification worth \$1M+ in client revenue.
    \item Moved the company from mailed checks to ACH across 200+ vendors; cut payment turnaround from 5--7 days to one business day, eliminating \$1,500+/year in mailing costs.
\end{itemize}}}

\vspace{3pt}

\needspace{5\baselineskip}
\item{\cventry{2023--2024}{Program Manager}{Giving Children Hope}{Buena Park, CA}{}{\vspace{1pt}
\begin{itemize}
    \item Managed weekly distribution of 350,000+ lbs of food to 250+ families; built a standardized allocation model to handle demand variability.
    \item Coordinated with 50+ schools to distribute 10,000+ toys to 1,500 children, designing the framework for equitable allocation across sites.
\end{itemize}}}

\vspace{3pt}

\needspace{5\baselineskip}
\item{\cventry{2022}{Public Health Intern}{Vive Peru}{Trujillo, Peru}{}{\vspace{1pt}
\begin{itemize}
    \item Co-led a dietary intervention targeting anemia (15\% prevalence reduction in one month); delivered medication and vaccinations to 250+ people, conducting all outreach in Spanish.
\end{itemize}}}

\end{itemize}

% ============================================================
%     EDUCATION
% ============================================================

\section{Education}
\vspace{1pt}
\begin{itemize}

\needspace{4\baselineskip}
\item{\cventry{2019--2023}{BA, Neuroscience \& Behavior (Minor: Business Economics)}{University of Notre Dame}{Notre Dame, IN}{}{\vspace{1pt}
GPA 3.63/4.00. Studied abroad at Trinity College Dublin. Youth tutor, MC3 Mentors.
}}

\end{itemize}

% ============================================================
%     LANGUAGES
% ============================================================

\section{Languages}
\vspace{1pt}
\begin{itemize}
\item English (native), Spanish (professional proficiency).
\end{itemize}

% ============================================================
%     LEADERSHIP & INTERESTS
% ============================================================

\section{Leadership \& Interests}
\vspace{1pt}
\begin{itemize}
\item Youth Basketball Coach, Play Like a Champion (2022) --- built a neuroscience-based, trauma-informed coaching workshop for five coaches; coached 20 players.
\item Karate (black belt), golf, sports analytics \& +EV modeling, Stoic philosophy.
\end{itemize}

% ============================================================
%     REFERENCES
% ============================================================

\section{References}
\vspace{1pt}
\begin{itemize}
\item{Available upon request.}
\end{itemize}

\end{document}
